Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-03-05 main.Rmd
content cut from applications

**Example:** Let us use Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2} to compute the multiple-order-up granularity hour_month and day_year for the Gregorian calendar considered.

@@

Even when there are no rarely occuring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations based on density should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators (see \autoref{eq:MSE})

<!--  shows that the variance of both $\hat{f(x)}$ <!--and $\hat{q(u)}$--> is a function of the sample size $n$. -->

@@

These cyclic granularities are a function of the index variable and are computed based on if they are circular (Section \ref{sec:circular-gran-def}), pseudo-circular (Section \ref{sec:quasi-circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def}). If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, quarter, semester, year), the following cyclic time granularities can be considered for this analysis. The interval of this tsibble is 30 minutes, and hence the temporal granularities may range from half-hour to year.

```{r search, echo=TRUE}
library(gravitas)
smart_meter %>% search_gran()
```

@@

If these options are considered too many, the most coarse temporal unit can be set to a “month”.

```{r search_limit1, echo=TRUE}
smart_meter10 %>%
  search_gran(highest_unit = "month")
```

@@

Also, some intermediate temporal units that might not be pertinent to the analysis can be removed from the list of cyclic granularities we want to look at.

@@

# filter(fielding_wckts %in% c(0,1)) %>%
cricket_data %>% prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
) + ggtitle("") + geom_boxplot(width = 0.5, aes(colour = lag_field)) + ylim(0,4.5)
```

@@

# Appendix

```{r granadvice, echo = TRUE, warning=FALSE, message=FALSE}
smart_meter10 %>%
  filter(customer_id %in% c(10017936)) %>%
  gran_advice(
    "wknd_wday",
    "hour_day"
  )
```

>>>>

**Example:** Let us use Equations \ref{eq:multifromsingle-quasi1} and \ref{eq:multifromsingle-quasi2} to compute the multiple-order-up granularity hour-of-month and day-of-year for the Gregorian calendar considered.

@@

Even when there are no rarely occuring events, number of observations might vary hugely within or across each facet. This might happen due to missing observations in the data or uneven locations of events in time domain. In such cases, the statistical transformations based on density should be used with caution as sample sizes would directly affect both the variance and consequently the confidence interval of the estimators (see \autoref{eq:MSE}) <!--  shows that the variance of both $\hat{f(x)}$ <!--and $\hat{q(u)}$--> is a function of the sample size $n$.

@@

These cyclic granularities are a function of the index variable and are computed based on if they are circular (Section \ref{sec:circular-gran-def}), pseudo-circular (Section \ref{sec:quasi-circular-gran-def}) or aperiodic (Section \ref{sec:aperiodic-gran-def}). If we consider conventional time deconstructions for a Gregorian calendar (second, minute, half-hour, hour, day, week, fortnight, month, year), the following cyclic time granularities can be considered for this analysis. The interval of this tsibble is 30 minutes, and hence the temporal granularities may range from half-hour to year.

```{r search, echo=FALSE}
library(gravitas)
smart_meter %>% search_gran(filter_out = c("semester", "quarter"))
```

@@

If these options are considered too many, the most coarse temporal unit can be set to a “month”. Also, some intermediate temporal units that might not be pertinent to the analysis can be removed from the list of cyclic granularities we want to look at.

<!-- CONTENT CUT -->
<!-- # ```{r search_limit1, echo=TRUE} -->
<!-- # smart_meter10 %>% -->
<!-- #   search_gran(highest_unit = "month") -->
<!-- # ``` -->

@@

@@

# filter(fielding_wckts %in% c(0,1)) %>%
cricket_data %>% prob_plot("over", "lag_field",
  hierarchy_model,
  response = "run_rate",
  plot_type = "violin",
) + ggtitle("") + geom_boxplot(width = 0.5, aes(colour = lag_field)) + ylim(0, 4.5)
```

@@

<!-- # Appendix -->

<!-- ```{r granadvice, echo = TRUE, warning=FALSE, message=FALSE} -->
<!-- smart_meter10 %>% -->
<!--   filter(customer_id %in% c(10017936)) %>% -->
<!--   gran_advice( -->
<!--     "wknd_wday", -->
<!--     "hour_day" -->
<!--   ) -->
<!-- ``` -->
